D3064R0: How to Avoid OOTA Without Really Trying

### 2024-03-05 ootavacuous.tex
Abstract: Further rewording of second-to-last sentence
Suggested-by: Alan Stern <stern@rowland.harvard.edu>
Signed-off-by: Paul E. McKenney <paulmck@kernel.org>

	We focus on shared-memory programs and
	C++ implementations based on traditional compilers and
	computing hardware, including CPUs and GPGPUs.
	This context permits us to consider the detailed relations
	between source code and machine code required by the restricted
	nature of volatile atomic accesses.
	The OOTA problem and the related challenge of coming to grips
	with semantic dependency are much more tractable at the hardware
	level than at the source level, thanks to existing formal
	hardware models.
	We show that these models' constraints prevent OOTA cycles
	that involve only volatile atomics from occurring in
	undefined-behavior-free C++ programs (under these implementations).
	We also extend this work to nonvolatile atomics by defining
	``quasi-volatile'' behavior that we expect C++ implementations
	will adhere to if they perform single-thread analysis.
\end{abstract}

>>>>

	We focus on shared-memory programs and
	C++ implementations based on traditional compilers and
	computing hardware, including CPUs and GPGPUs.
	This context permits us to consider the detailed relations
	between source code and machine code required by the restricted
	nature of volatile atomic accesses.
	The OOTA problem and the related challenge of coming to grips
	with semantic dependency are much more tractable at the hardware
	level than at the source level, thanks to existing formal
	hardware models.
	We show that these models' constraints prevent OOTA cycles
	from occurring in undefined-behavior-free C++ programs running
	on compiler-based implementations, provided the cycles involve
	only volatile atomics.
	We also extend this work to nonvolatile atomics by defining
	``quasi-volatile'' behavior that we expect C++ implementations
	will adhere to if they perform single-thread analysis.
\end{abstract}
